Synthesizing Symmetric Lenses

### 2018-07-10 papers/SymmetricLenses/main.tex

\subsection{Simple Symmetric Lenses}
A simple symmetric lens between formats described by types $X$ and $Y$ is
defined by four functions.\bcp{I think a picture would be helpful. I can
  probably make one pretty easily by tweaking the one from the original
  symmetric paper.} \afm{That would be awesome.}

>>>>

\subsection{Simple Symmetric Lenses}
A simple symmetric lens between formats described by types $X$ and $Y$ is
defined by four functions.
